Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-17 talk/iwtc11/paper.tex
small improvements, write para about benchmarks

For all JIT:ed runs (PyPy and Psyco) 3 iterations were run to warm up the JIT,
followed by 10 iterations for averaging. For GCC and CPython, 5 iterations
were run. In all cases, the standard deviation is very low, making benchmarks
very well reproducible.

XXX discuss some more, explain why gcc is faster
XXX we need Psyco numbers

>>>>

For PyPy 10 iterations were run, prefaced with 3 iterations for warming up.
Due to benchmarks taking large amounts of time on CPython, only one run
was performed, prefaced with one warmup run for Psyco.
For GCC 5 iterations
were run. In all cases, the standard deviation is very low, making benchmarks
very well reproducible.

We can observe that PyPy (even without loop peeling) is orders of magnitude
faster than either CPython or Psyco. This is due to the JIT compilation
advantages and optimizations we discussed in XXX [ref to other paper]. Loop
peeling gives an additional XXX on average, which makes benchmark times
comparable with native-compiled C code. Missing performance we attribute to
the relative immaturity of PyPy's JIT assembler backend as well as missing
optimizations, like instruction scheduling.
